---
title: "Untitled"
author: "Kaizad F. Patel"
date: "5/26/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is regular text

```{r}
library(tidyverse)
library(palmerpenguins)
```

Dealing with R:

1. in-text R usage

One plus two equals `1+2`.

2. Create an R chunk using ```
you need to specify "r" as the coding language

```{r}
names(iris)
```

Hide the code using `echo = FALSE`
```{r, echo=FALSE}
names(iris)
```

Hide the output
```{r, include=FALSE}
names(iris)
```

To skip the chunk altogether (i.e. skip the evaluation), use `eval = FALSE`

```{r, eval=FALSE, echo=FALSE}
names(iris)
```

```{r, fig.height=5, fig.width=7}
plot(penguins)
```

---


Headers

# H1
## H2
### H3
#### H4
##### H5
###### H6
regular text

---

In-text formatting.
**bold**, *italics*, ~~strikethrough~~, ~subscript~, <sup>superscript</sup>

Fe<sup>+3</sup>

---

tables

1. creating tables manually in markdown

| colA | colB |
|-----|------|
|1 | 2 |
|1 | 2 |

2. create tables using knitr::kable()

```{r}
a = penguins %>% 
  head() %>%  knitr::kable()
```

object = summary_table()

in markdown

loadd(object)
readd(object) %>% 
change1 %>% 
change2 %>% 
knitr::kable()

---

---


<details>
  <summary>Click to open</summary>
  
  this is the text.
  
  this is more text.
  
  
  this is the text.  
  this is more text.
</details>